\documentclass[a4, 12pt]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{bibentry}

%opening
\title{American Politics Pop Quiz}
\author{}
\date{}

\begin{document}

\maketitle
\nobibliography*

\noindent Without using the internet or any resource other than your own brain, try to guess answers to each of the following questions.

\begin{enumerate}
\item In what year was the U.S. Constitution authored?
\item What institution proposes legislation in the federal government?
\item What are the two chambers of the U.S. Congress?
\item Which chamber has more members?
\item How many Senators are there from each U.S. state?
\item What institution determines the constitutionality of state and federal laws?
\item How are U.S. Senators elected to office?
\item How are members of the U.S. House of Representatives elected?
\item How is the President of the United States elected to office?
\item How are candidates in U.S. Presidential elections chosen?
\item Who is eligible to be the President of the United States?
\item What responsibilities does the Vice President of the United States have?
\item How much money can candidates spend on their election campaigns?
\item What is the Second Amendment to the U.S. Constitution?
\item Who in the federal government has the power to declare war?
\item What is the size (in U.S. dollars) of the U.S. economy (GDP)?
\item What is the size (in U.S. dollars) of the U.S. federal budget?
\item What is the size (in U.S. dollars) of the U.S. federal government debt?
\item What percentage of the U.S. federal budget is spent on the military?
\item What percentage of the U.S. federal budget is spent on social welfare programs?
\item What percentage of the U.S. federal budget is spent on education?
\item How is the U.S. federal government authorized to raise revenue?
\item What is the ``filibuster''?
\item Which institution is more powerful, the President or Congress?
\item Do U.S. states have the ability to ignore or amend federal legislation?
\item How are judges on U.S. federal courts appointed?
\item How are judges in state and local courts appointed?
\item How long can a U.S. politician remain in office?
\item In 1978, 1995--6, and 2013, the federal government ``shut down.'' What does this mean?
\item When was the last time both chambers of the U.S. Congress approved a budget resolution?
\item What is a ``third party''?
\item What was the turnout rate in the 2012 U.S. Presidential election?
\item What is ``polarization''? Is the United States polarized?
\item What is the highest U.S. federal tax rate on personal income/salary?
\item Denmark has a Gini index of 24. What is the Gini index for the United States? % 45
\item What is Social Security?
\item What types of national health care or national health insurance does the United States have?
\item How is tertiary (University) education in the United States financed?
\item When did African Americans receive the right to vote in the United States?
\item When did women receive the right to vote in the United States?
\item What percentage of the U.S. population was born outside of the United States?
\item What percentage of the U.S. population is African American?
\item What is/are the official language(s) of the United States?
\item What is the official religion of the United States?
\item How many firearms (guns) are there in the United States?
\item How many people have been executed in the United States since 1976?
\item What is the minimum age for a convicted murderer to be eligible for the death penalty?
\item What is \textit{Roe v. Wade}?
\item Who is Anthony Kennedy?
\item In contemporary American politics, what is the distinction between a political ``liberal'' and a political ``conservative''?
\end{enumerate}


\end{document}
