\documentclass[12pt]{beamer} %Makes presentation

\input{preamble}

\title{Wrap-Up}

\date[]{December 11, 2014}

\begin{document}

\frame{\titlepage}

\frame{\tableofcontents}

\section{Procedural Stuff}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Exam}
	\begin{itemize}\itemsep2em
		\item December people: You should have received an email about the synopsis submission process
			\begin{itemize}
				\item Synopsis due tomorrow
				\item Exam next Friday (Dec. 19) probably in the morning
			\end{itemize}
		\item If not, email Tina Aronro (tina@au.dk)\\ and CC me (tleeper@ps.au.dk)
		\item January people: Same deal, but in January
	\end{itemize}
}


\frame{
	\frametitle{Exam Preparation}
	\begin{itemize}\itemsep2em
		\item Two practice exam questions
	\end{itemize}	
}


\section{Polarization (cont.)}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Polarization}
	\begin{itemize}\itemsep2em
		\item What does polarization mean?
		\item What consequences does it have for politics?
		\item Is polarization good or bad for the United States?
	\end{itemize}
}


\section{Dramatic Finale}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Where have we been?}
	\begin{itemize}
		\item American values
		\item The American Founding
		\item Congress
		\item The Presidency and executive branch
		\item Courts
		\item States and local governments
		\item Parties and partisanship
		\item Campaigns and elections
		\item Public policy
		\item Race and other inequalities
		\item Polarization
	\end{itemize}
}

\frame{
	\frametitle{What themes run through this?}
	\begin{itemize}\itemsep1em
		\item<2-> Dysfunctional politics
		\item<3-> Low levels of citizen influence
		\item<4-> Intentionally diffuse, conflictual institutions
		\item<5-> Importance of individual rights
		\item<6-> Ambiguous constitutional constraints on politics
		\item<7-> Disagreement and political differences
	\end{itemize}
}


\frame{
	\frametitle{Given what you've learned\dots}
	\begin{itemize}\itemsep2em
		\item<1-> What, if anything, can you take away from this course that might help you to understand other political systems (e.g., Denmark, etc.)?
		\item<2-> What do you still want to know about American politics?
	\end{itemize}
}


\section{Evaluations}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Course Evaluations}
	\begin{itemize}\itemsep2em
		\item Do you have any feedback for me regarding the course?
		\item<2-> Official course evaluations due Dec 17
		\item<2-> Complete online at:\\ \url{http://www.survey-xact.dk/LinkCollector?key=KW5CHWRX1P15}
	\end{itemize}
}





\frame{}

\end{document}
